### 2013-06-05 doc/pgas13/evaluation.tex
Add plots for BFS and CC performance.

>>>>

\paragraph{HashSet and HashMap}
The GlobalHashSet and GlobalHashMap have the same synchronization strategy (serialization happens at each hashed location).

\subsection{Application Kernel Performance}
The impetus for this work was that naive implementations of standard data structures are insufficient for use in high-performance kernels.

\paragraph{Breadth-First Search}
\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\textwidth]{data/plots/bfs_perf.pdf}
  \caption{BFS on a Graph500-spec graph of scale 26 (64 million vertices, 1 billion edges), with the direction-optimizing BFS algorithm. Performance is shown in millions of Traversed Edges Per Second (MTEPS).}
  \label{fig:bfs_perf}
\end{figure}

\paragraph{Connected Components}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\textwidth]{data/plots/cc_perf.pdf}
  \caption{Connected Components on the same scale 26 Graph500 graph. Performance is measured in TEPS, parameterized only by the total number of edges in the graph, regardless of the algorithm used.}
  \label{fig:cc_perf}
\end{figure}
